Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-03 ms.tex

To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}. In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal15}. In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for further details.

\subsubsection{Simulation}
We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters).

@@

In standard HOD models, there are two types of galaxies: centrals and satellites. The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively. $P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo is supposed to have only either zero or one central galaxy. So the occupation statistics of central galaxies is specified by its first moment, which we model as

>>>>

To generate predictions for galaxy clustering, we directly populate dark matter halos with mock galaxies using {\tt Halotools}. In this section we review the ``standard" HOD-style model used in the present work, and in the following section we use the Decorated HOD model described in \citet{hearin_etal16}. In both cases, we will only briefly review the salient features of our methodology here; interested readers can always refer to {\tt halotools.readthedocs.io} for further details.

\subsubsection{Simulation}
We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters). yadda yadda yadda.

@@

In standard HOD models, there are two types of galaxies: centrals and satellites. The galaxy-halo connection is specified in terms of $P(\ncen|\mvir)$ and $P(\nsat|\mvir),$ the probability that a halo of mass $\mvir$ hosts $\ncen$ central and $\nsat$ satellite galaxies, respectively. $P(\ncen|\mvir)$ is typically a nearest-integer distribution, as a host halo is supposed to have only either zero or one central galaxy. So occupation statistics of central galaxies are specified by the first moment, which we model as
